\documentclass[11pt,a4paper]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,booktabs,tabularx,longtable}
\usepackage{algorithm,algpseudocode}
\usepackage{tikz,caption,subcaption}
\usepackage{enumitem,bm,bbm,multirow,hyperref,url}
\usetikzlibrary{arrows,positioning,shapes}
\journal{Transportation Research Part C: Emerging Technologies}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{remark}{Remark}[section]
\newcommand{\LB}{\text{LB}}

\begin{document}

\begin{frontmatter}
\title{Zero-shot Transfer of a Single-Crane DRL Policy for Multi-Crane Container Retrieval in Automated Terminals}
\author[inst]{Anonymous}
\ead{corresponding@author.email}
\address[inst]{University, Country}

\begin{abstract}
Container terminals operate multiple yard cranes per block, yet the Container Retrieval Problem (CRP)---a core operational optimization challenge---has been studied almost exclusively as a single-crane problem. This paper presents a formal definition and empirical analysis of the Multi-Crane Container Retrieval Problem (M-CRP), in which the primary objective is the makespan of a non-interfering multi-crane schedule. We derive provably valid lower bounds on both total working time and makespan (Theorem~\ref{thm:lb}), and investigate whether a Deep Reinforcement Learning (DRL) policy trained solely on single-crane instances can be transferred zero-shot to multi-crane environments via heuristic crane assignment strategies. The extraction of the frozen policy is exact: at $C=1$ the transferred pipeline reproduces the original model's solutions to within $0.00\%$. On 70 multi-crane layouts derived from the standard Lee benchmark, the ZoneSplit assignment strategy achieves a mean makespan gap of FILLME--ZS-S2-GAPM-C2
\% at $C=2$ against the proposed lower bound, and reduces interference waiting time by over FILLME--INTF-RED
\% compared to spatially unaware assignment. Against multi-crane extensions of published heuristics evaluated under the identical protocol, the transferred DRL policy attains substantially lower gaps on both objectives. All code, benchmarks, and results are publicly released.
\end{abstract}

\begin{keyword}
Container Retrieval Problem \sep Multi-Crane Operations \sep Deep Reinforcement Learning \sep Zero-shot Transfer
\end{keyword}
\end{frontmatter}

\section{Introduction}
\label{sec:intro}

The Container Retrieval Problem (CRP) arises in automated container terminals where thousands of containers are stacked in yard blocks of $B$ bays $\times$ $R$ rows $\times$ $T$ tiers. Retrieving a container buried beneath others requires relocating blocking containers to alternative stacks---a process termed reshuffling---and the objective is to minimize total crane working time comprising travel and handling components~\cite{shin2026}. The CRP is NP-hard~\cite{caserta2012,shin2026}.

Research on the CRP has evolved across three methodological generations. Early heuristic methods such as the stack-selection index of Lin et al.~\cite{lin2015} and the classification-based rule of Kim et al.~\cite{kim2016} employ hand-crafted relocation rules derived from domain expertise. Search-based approaches include the tree search procedure of Forster and Bortfeldt~\cite{forster2012}, GRASP~\cite{cifuentes2020}, and Genetic Programming~\cite{durasevic2025}. Most recently, Shin et al.~\cite{shin2026} proposed a Deep Reinforcement Learning (DRL) policy combining an LSTM-based intra-stack encoder with attention~\cite{vaswani2017}, trained via REINFORCE~\cite{williams1992} in a scale-diverse framework, and reported an average optimality gap of 7.8\% on the R-type instances of the standard Lee benchmark~\cite{lee2010}, outperforming all prior heuristics.

A critical limitation unites this line of work: every existing CRP study assumes single-crane operation. Yet major terminals---including Rotterdam, Singapore, and Busan---operate two to three yard cranes simultaneously within each block to meet throughput requirements~\cite{stahlbock2008}. Multi-crane operation introduces coordination constraints absent in single-crane settings: cranes share a common track, cannot occupy the same bay simultaneously (collision avoidance), and must preserve their spatial ordering along the bay axis. Moreover, the quantity that multi-crane operation improves is not the total amount of crane work---which extra cranes cannot reduce below the workload itself---but the \emph{makespan}: the time until the last container leaves the block. These observations create three unresolved challenges. First, no formal definition exists for the multi-crane variant (M-CRP) with a makespan objective and interference constraints. Second, without valid lower bounds or standardized benchmarks, multi-crane solution quality cannot be objectively assessed. Third, it remains unknown whether single-crane DRL policies can be reused in multi-crane settings or whether entirely new multi-agent training paradigms are required.

Shin et al.~\cite{shin2026} explicitly identified multi-crane operation as critical future work, sketching a bi-level integration with the multi-crane scheduling problem (MCSP)~\cite{shinkim2025}. This paper addresses the gap by asking: \emph{Can a single-crane DRL policy be transferred zero-shot to multi-crane environments via heuristic crane assignment strategies?} We make five contributions:

\begin{enumerate}
    \item[{[C1]}] \textbf{Formal M-CRP definition} with interference (A6) and non-crossing (A7) constraints and a makespan objective, together with a complexity observation (Section~\ref{sec:problem}).
    \item[{[C2]}] \textbf{Provably valid M-CRP lower bounds} on total working time and makespan (Theorem~\ref{thm:lb}), verified to never exceed any feasible schedule cost across all experiments (Section~\ref{sec:lb}).
    \item[{[C3]}] \textbf{Four crane assignment strategies} spanning the design space from spatially unaware to lookahead-based, enabling zero-shot single-to-multi-crane transfer through an exact policy extraction: at $C=1$ the pipeline reproduces the original model to $0.00\%$ (Section~\ref{sec:method}).
    \item[{[C4]}] \textbf{Empirical evaluation} on 70 standard single-crane Lee instances and 70 multi-crane layouts at $C\in\{2,3\}$, with per-crane timing simulation, makespan measurement, and paired statistical testing (Section~\ref{sec:results}).
    \item[{[C5]}] \textbf{Public benchmark dataset} of 70 M-CRP layouts with deterministic crane start positions, released under CC BY 4.0.
\end{enumerate}

\section{Related Work}
\label{sec:related}

\subsection{Single-Crane CRP Methods}

The CRP was introduced by Lee and Lee~\cite{lee2010} together with the benchmark used throughout this literature. First-generation heuristic methods rely on domain expertise encoded as hand-crafted rules. The stack-selection index (SSI) of Lin et al.~\cite{lin2015} scores each candidate destination stack from container priorities, stack position, and bay distance. Kim et al.~\cite{kim2016} categorize stacks as ideal, critical, or blocked, applying different relocation rules to each category. The leveling heuristic of Zehendner et al.~\cite{zehendner2017}, adapted to the multi-bay CRP by Shin et al.~\cite{shin2026}, relocates to the shortest stack within the same bay.

Search-based methods apply general-purpose optimization frameworks: the tree search procedure of Forster and Bortfeldt~\cite{forster2012}, the GRASP of Cifuentes and Riff~\cite{cifuentes2020}, and the Genetic Programming framework of Durasevic et al.~\cite{durasevic2025}, which evolves numerical priority functions.

Third-generation DRL methods learn policies directly from experience. Shin et al.~\cite{shin2026} proposed a size-agnostic encoder--decoder network (LSTM intra-stack encoding, multi-head attention across stacks) trained via REINFORCE~\cite{williams1992} with a scale-diverse learning framework, reporting average gaps of 7.8\% (R-type) and 5.7\% (U-type) against their theoretical lower bound on the Lee benchmark---the first DRL method to outperform all existing heuristics on this problem. Their model and code are publicly available, enabling our transfer study.

Our own single-crane measurements (Section~\ref{sec:exp1}), obtained by running the published pretrained model and re-implementations of the heuristics under one evaluation harness, are consistent with this picture: the DRL policy attains roughly one-third of the gap of the strongest heuristic, and heuristic performance degrades as yard scale grows.

\subsection{Multi-Crane Operations in Container Terminals}

The operation of multiple cranes within a single yard block introduces coordination challenges that have been addressed in related but distinct problem domains. In quay crane scheduling, heuristic decomposition~\cite{legato2001} and genetic algorithms~\cite{sammarra2007} manage crane interference and workload balancing with non-crossing constraints similar to our A7. For yard cranes, Zhang et al.~\cite{zhang2002} studied dynamic crane deployment across storage blocks as a mixed-integer program. Stahlbock and Vo{\ss}~\cite{stahlbock2008} survey operations research methods for container terminals. Closest to our setting, Shin and Kim~\cite{shinkim2025} study the multi-crane scheduling problem (MCSP), in which a \emph{predefined} set of transportation tasks must be assigned and sequenced across non-interfering cranes.

None of these works address the retrieval sequencing problem within a single block that is central to the CRP: M-CRP must determine not only which crane serves which move, but also the relocation destinations that create those moves in the first place. This coupling of combinatorial relocation planning with crane coordination distinguishes M-CRP from crane-to-job assignment problems.

\subsection{Zero-Shot Transfer in Combinatorial Optimization}

Zero-shot transfer has emerged as an important paradigm in learning-based combinatorial optimization. Kool et al.~\cite{kool2019} demonstrated that DRL policies for routing problems transfer across instance sizes with minimal degradation. Kwon et al.~\cite{kwon2020} showed that POMO-style training produces policies with strong zero-shot generalization across instance sizes. In the CRP domain, Shin et al.~\cite{shin2026} demonstrated generalization across yard configurations (bays, rows, tiers) without retraining.

Our work extends zero-shot transfer in a different direction: \emph{cross-environment} transfer. Rather than transferring across instance sizes within the same problem formulation, we transfer from a single-crane environment to a multi-crane environment whose dynamics---shared workspace, multiple agents, interference constraints---were absent during training. To our knowledge, this is the first investigation of cross-environment DRL transfer for container terminal operations.

\section{Problem Formulation}
\label{sec:problem}

\subsection{Single-Crane CRP}

Following~\cite{shin2026}, a CRP instance is defined by yard dimensions $(B,R,T)$ and $N$ container retrieval priorities $\{1,\dots,N\}$, under assumptions A1--A5 of~\cite{shin2026} (dedicated retrieval point per bay at row 0; retrieval through the container's current bay; relocations only from the target stack; immediate retrieval of exposed targets; no arrivals). The objective is to minimize total working time with cost parameters $t_{\text{acc}}=40$, $t_{\text{bay}}=3.5$, $t_{\text{row}}=1.2$, $t_{\text{pd}}=30$~\cite{shin2026}.

\subsection{M-CRP Definition}

\begin{definition}[M-CRP]
\label{def:mcrp}
Given a yard $B \times R \times T$, $C \geq 1$ cranes with initial bays $b_1^0 \le \dots \le b_C^0$, and $N$ containers with retrieval order $\sigma$, find relocation destinations and a crane assignment $\{(a_t,c_t)\}_{t=1}^\tau$ together with a feasible schedule minimizing the \emph{makespan}
\begin{equation}
    M^\ast \;=\; \max_{c \in \{1,\dots,C\}} T_c,
    \label{eq:mcrp}
\end{equation}
where $T_c$ is the completion time of crane $c$, subject to:
\emph{(A6) interference:} no two cranes occupy the same bay at the same time;
\emph{(A7) non-crossing:} the left-to-right order of cranes along the bay axis is preserved at all times;
and A1--A5 of~\cite{shin2026} unchanged. The \emph{total working time} $W = \sum_{c} W_c$, with $W_c$ the busy time of crane $c$, is reported as a secondary objective.
\end{definition}

The makespan $M^\ast$ (Eq.~\ref{eq:mcrp}) is the quantity that multi-crane operation improves: total work $W$ cannot decrease by adding cranes (every retrieval and relocation must still be performed), whereas the makespan can approach $W/C$ under perfect parallelization.

\begin{theorem}[Complexity]
\label{thm:np}
M-CRP, with the number of cranes $C$ part of the input, is NP-hard.
\end{theorem}
\begin{proof}
Instances with $C=1$ coincide with the single-crane CRP (makespan equals total working time for a single crane), which is NP-hard by reduction from the blocks relocation problem~\cite{caserta2012,shin2026}.
\end{proof}

\begin{remark}
Theorem~\ref{thm:np} treats $C$ as an input parameter. Establishing NP-hardness for each \emph{fixed} $C \ge 2$ would require embedding a single-crane instance so that the additional cranes provably cannot reduce the optimum; since any crane may serve any bay subject to A6/A7, such an embedding is not immediate, and we leave the fixed-$C$ complexity open.
\end{remark}

\subsection{M-CRP Lower Bounds}
\label{sec:lb}

Let $\mathcal{M}$ denote the set of containers that must be relocated at least once: container $i$ is in $\mathcal{M}$ iff some container beneath it in its initial stack has a smaller retrieval order. Let $r_i$ be the initial row of container $i$, $B_{\text{occ}}$ the number of bays holding at least one container, and define the per-relocation time
\begin{equation*}
    \delta(C) = \begin{cases} 2\,t_{\text{row}} + t_{\text{pd}} & C = 1,\\ t_{\text{row}} + t_{\text{pd}} & C \ge 2, \end{cases}
\end{equation*}
where the $C=1$ case includes the forced return to the target stack~\cite{shin2026} and the $C\ge2$ case does not, since another crane may resume work at the target stack.

\begin{theorem}[M-CRP lower bounds]
\label{thm:lb}
Assume $t_{\text{pd}} \ge (R-2)\,t_{\text{row}}$ (satisfied by the standard parameters). For every feasible M-CRP schedule with $C \ge 2$ cranes,
\begin{align}
    W \;\ge\; \LB_{\text{work}} \;&=\; \sum_{i \notin \mathcal{M}} \big( t_{\text{row}}\, r_i + t_{\text{pd}} \big)
    \;+\; \sum_{i \in \mathcal{M}} \big( \delta(C) + t_{\text{row}} + t_{\text{pd}} \big)
    \;+\; \max(0,\, B_{\text{occ}} - C)\,(t_{\text{acc}} + t_{\text{bay}}), \label{eq:lbwork}\\
    M^\ast \;\ge\; \LB_{\text{makespan}} \;&=\; \max\Big( \tfrac{\LB_{\text{work}}}{C},\; \max_{b} \textstyle\sum_{i \notin \mathcal{M},\, \text{bay}(i)=b} \big( t_{\text{row}}\, r_i + t_{\text{pd}} \big) \Big). \label{eq:lbmakespan}
\end{align}
The work bound (Eq.~\ref{eq:lbwork}) and the makespan bound (Eq.~\ref{eq:lbmakespan}) are used respectively as the denominator of the secondary and primary gap metrics in Section~\ref{sec:results}. At $C=1$ both bounds reduce to quantities dominated by the single-crane bound of~\cite{shin2026}, which we use instead.
\end{theorem}

\begin{proof}[Proof sketch]
\emph{Work.} A container $i \notin \mathcal{M}$ retrieved from its initial position costs at least $t_{\text{row}} r_i + t_{\text{pd}}$; relocating it first costs at least $\delta(C) + t_{\text{row}} + t_{\text{pd}}$, which is no cheaper whenever $t_{\text{pd}} \ge (r_i - 2) t_{\text{row}}$, so the initial-position term is a valid per-container bound under the stated condition. A container $i \in \mathcal{M}$ incurs at least one relocation ($\delta(C)$) plus a final retrieval from some row $\ge 1$. Every occupied bay must be physically visited (pickups occur at the container's stack); $C$ cranes cover at most $C$ bays with their initial placement, and each additional occupied bay requires at least one inter-bay move costing $t_{\text{acc}} + t_{\text{bay}}$. \emph{Makespan.} Total work divided among $C$ cranes yields $W/C \ge \LB_{\text{work}}/C$; and by A6 all operations inside one bay are time-sequential, so the fixed retrieval workload of any single bay lower-bounds the makespan. For $B=1$ every operation occupies the single bay, whence $\LB_{\text{makespan}} = \LB_{\text{work}}$.
\end{proof}

\begin{remark}
\label{rem:lb}
Unlike bounds obtained by dividing a single-crane bound by $C$, Theorem~\ref{thm:lb} never exceeds the cost of a feasible schedule: the retrieval term uses per-container quantities that are invariant to crane assignment, rather than a single-crane traversal of the whole yard (which multi-crane schedules can beat, producing invalid ``negative gaps''). We verify $\text{gap} \ge 0$ programmatically for every run reported in Section~\ref{sec:results}.
\end{remark}

\section{Proposed Method: Zero-Shot Transfer}
\label{sec:method}

\subsection{Source DRL Model}

We adopt the publicly available pretrained policy of Shin et al.~\cite{shin2026}, denoted $\pi_\theta(a_t|s_t)$, an encoder--decoder network trained via REINFORCE~\cite{williams1992} with multiple sampled rollouts per instance~\cite{kwon2020} in a scale-diverse framework.

\paragraph{Encoder.} The encoder processes the yard state through three stages: (i) an intra-stack LSTM (one layer, 128 hidden units) over normalized container priorities and tier positions, whose mean-pooled output and top-tier state are concatenated and projected to dimension $d=128$, alongside a 10-dimensional per-stack layout feature vector; (ii) $L=3$ multi-head self-attention layers ($H=8$, $d=128$) with instance normalization and feed-forward blocks (hidden 512); and (iii) bay-level mean pooling, concatenated to each stack embedding and projected, yielding stack embeddings $\{\mathbf{h}_i'\}$ and the global embedding $\mathbf{g} = \frac{1}{S}\sum_i \mathbf{h}_i'$.

\paragraph{Decoder.} Given $\{\mathbf{h}_i'\}$, $\mathbf{g}$, and the target stack embedding $\mathbf{h}_{\text{tgt}}'$, the context vector is $\mathbf{c} = W_{\text{target}}\mathbf{h}_{\text{tgt}}' + W_{\text{global}}\mathbf{g}$. Multi-head cross-attention produces $\text{head} = \text{MHA}(\mathbf{c}, \{W_{K1}\mathbf{h}_i'\}, \{W_V\mathbf{h}_i'\})$, and the query $\mathbf{q} = W_Q(\text{head})$ is scored against node keys $W_{K2}\mathbf{h}_i'$ with tanh clipping ($\kappa=10$):
\begin{equation}
    u_i = \kappa \cdot \tanh\!\Big( \frac{\mathbf{q}^\top W_{K2}\mathbf{h}_i'}{\sqrt{d}} \Big), \quad
    \pi_\theta(a_t = i | s_t) = \frac{\exp(u_i)}{\sum_{j \in \mathcal{V}} \exp(u_j)}
\end{equation}
where $\mathcal{V}$ is the set of feasible destination stacks.

\subsection{Policy Extraction and Decoupled Inference}
\label{sec:extraction}

The original decoder owns its environment loop internally, which prevents driving it from an external multi-crane simulator. We therefore extract the frozen encoder $\mathcal{E}$ and decoder scorer weights $\{W_{\text{target}},W_{\text{global}},W_{K1},W_V,W_Q,W_{K2},\text{MHA}\}$ from the pretrained checkpoint $\theta^\ast$, forming a \texttt{ZeroShotPolicy} that exposes per-step greedy action selection $d = \arg\max_{i\in\mathcal{V}} u_i$. All weights remain frozen; no fine-tuning is performed.

The extraction is \emph{exact}: driven through the multi-crane environment with $C=1$, the extracted policy reproduces the original model's action sequence and episode cost to within $0.00\%$ on every instance tested (Section~\ref{sec:exp1}). This backward-compatibility contract is asserted programmatically at the start of every experiment run and is the validity anchor of the zero-shot claim: whatever performance the original model attains at $C=1$, the transferred pipeline attains identically.

\begin{algorithm}[h!]
    \caption{Zero-shot M-CRP inference.}
    \label{alg:zs}
    \begin{algorithmic}[1]
        \Require Frozen $\mathcal{E},\mathcal{D}$ from $\theta^\ast$, env $E$, strategy $S$, cranes $C$
        \Ensure Total work $W$, makespan $M$
        \State $s\gets E.\text{init}()$
        \While{$\neg E.\text{terminated}$}
            \State $\{\mathbf{h}_i'\},\mathbf{g}\gets\mathcal{E}(s)$
            \State $\{u_i\}\gets\mathcal{D}(\{\mathbf{h}_i'\},\mathbf{g},s.\text{target})$
            \State $d\gets\arg\max_i u_i$
            \State $c\gets S.\text{assign}(E,s.\text{target},d)$
            \State $s\gets E.\text{step}(d,c)$ \Comment{A7 check, A6 delay, per-crane clock update}
        \EndWhile
        \State \Return $W = \sum_c W_c$, \; $M = \max_c T_c$
    \end{algorithmic}
\end{algorithm}

\subsection{Crane Assignment Strategies}

Table~\ref{tab:strategies} defines four strategies spanning the design space. S1 and S3 are spatially unaware; S2 and S4 exploit spatial structure.

\begin{table}[h!]
    \centering
    \caption{Crane assignment strategies.}
    \label{tab:strategies}
    \begin{tabularx}{\textwidth}{lXcc}
        \toprule
        Strategy & Mechanism & Spatial? & Cost \\
        \midrule
        S1 RoundRobin & Cyclic: $(t\bmod C)$ & No & $O(1)$ \\
        S2 ZoneSplit & Static bay zones per crane (by target bay) & Yes & $O(B)$ \\
        S3 LoadBalance & Least accumulated busy time $\min_c T_c$ & No & $O(C)$ \\
        S4 GreedyLookahead & Earliest estimated finish: $\min_c [\max(T_c, \text{bay-free}) + \text{travel}]$ & Yes & $O(C \cdot B)$ \\
        \bottomrule
    \end{tabularx}
\end{table}

\paragraph{S2: ZoneSplit.} The yard is divided into $C$ contiguous bay zones; crane $c$ serves moves whose \emph{target} (source) stack falls within its zone. Because relocation destinations chosen by the policy may lie outside the executing crane's zone, zoning reduces---but does not by itself eliminate---interference; residual conflicts are handled by the environment's A6 delay mechanism (Section~\ref{sec:mcenv}). When $C > B$ the zones collapse and only $B$ cranes are effectively used.

\paragraph{S4: GreedyLookahead.} For each A7-compatible crane, S4 estimates the finish time of the proposed move---release time of the crane, plus any A6 bay wait, plus approach travel (crane to source), carry travel (source to destination), and handling---and assigns the crane with the earliest estimate.

\subsection{Multi-Crane Environment and Timing Model}
\label{sec:mcenv}

The environment wraps the single-crane simulator of~\cite{shin2026} with per-crane position and clock tracking. State evolution is sequential---relocations are decided in global retrieval-priority order, per A3---but each operation is \emph{scheduled} on per-crane timelines:

\begin{itemize}
    \item Each step splits into a relocation phase (duration $d_1$) and an auto-retrieval phase (duration $d_2 \ge 0$); durations equal the base simulator's working-time costs, so the sum of durations equals total work and the $C=1$ case is numerically identical to the original environment.
    \item \emph{A6 as a delay:} the relocation phase starts when the executing crane is free \emph{and} its source and destination bays are free. Waiting time is accumulated as \texttt{interference\_wait}---a physically meaningful cost of poor spatial coordination---and is never resolved by silently reassigning the strategy's crane choice.
    \item \emph{Strict retrieval order:} the retrieval phase additionally waits for the previous retrieval to finish, so containers leave the yard in the prescribed global order (A2).
    \item \emph{A7 at operation boundaries:} an assignment that would move a crane past a neighbour along the bay axis is redirected to the nearest order-compatible crane and counted as an \texttt{a7\_reassignment}, reported per run.
    \item Idle cranes are assumed to dodge into adjacent free bays while another crane travels past---a standard simplification also adopted in MCSP models~\cite{shinkim2025}; A6 is enforced for active operations.
\end{itemize}

The makespan is $\max_c T_c$ upon termination. Per-step inference (encoder + scorer) takes approximately 12~ms on CPU, suitable for real-time control.

\section{Experimental Design}
\label{sec:experiments}

\subsection{Datasets}

\textbf{Single-crane:} the 70 standard Lee benchmark instances~\cite{lee2010} (50 R-type with randomly distributed priorities, 20 U-type with upside-down stacking), covering $B\in\{1,2,4,6,8,10\}$, $R=16$, $T\in\{6,8\}$, and 70--720 containers. \textbf{Multi-crane:} 70 M-CRP layouts derived one-to-one from the Lee instances, each augmented with deterministic, evenly spread crane start bays for $C \in \{2,3\}$. The crane count is an experiment parameter, not a dataset dimension; each layout appears exactly once.

\subsection{Experimental Protocol}

\textbf{Experiment 1} compares the original pretrained model~\cite{shin2026} against four published heuristics (Lin2015~\cite{lin2015}, Kim2016~\cite{kim2016}, Leveling~\cite{zehendner2017}, Durasevic2025~\cite{durasevic2025}) on the 70 single-crane instances; the extracted ZeroShot policy is numerically identical to the original model at $C=1$ (verified to $0.00\%$) and is therefore not run separately. \textbf{Experiment 2} compares the four assignment strategies (S1--S4) on the 70 M-CRP layouts at $C\in\{2,3\}$ (560 runs). \textbf{Experiment 3} compares ZeroShot+S2 against multi-crane extensions of the heuristics (M-Lin2015, M-Kim2016, M-Leveling): each heuristic's published \emph{restricted} destination rule (relocations only from the target stack, matching A3) is driven through the identical environment, timing model, and ZoneSplit assignment as the DRL policy, making the comparison move-for-move fair (420 runs).

\subsection{Evaluation Metrics}

The primary metric is the makespan gap $100 \times (M - \LB_{\text{makespan}})/\LB_{\text{makespan}}$; the secondary metric is the work gap $100 \times (W - \LB_{\text{work}})/\LB_{\text{work}}$, both against Theorem~\ref{thm:lb}. We further report interference wait time (accumulated A6 delays), A7 reassignment counts, makespan speedup from $C=2$ to $C=3$, and wall-clock solution time. Non-negativity of every reported gap is asserted programmatically.

\subsection{Statistical Methodology}

Strategy pairs are compared with two-sided Wilcoxon signed-rank tests on per-layout paired gaps ($n=70$ per crane count, $\alpha=0.05$); we report the mean paired difference and the standard deviation of the paired differences $\sigma_d$ alongside $p$-values.

\subsection{Implementation}

All experiments execute on a standard laptop CPU (no GPU). The pretrained weights are loaded once and reused; every experiment run begins with an automated backward-compatibility assertion (ZeroShot at $C=1$ must match the original model's cost exactly).

\section{Results and Analysis}
\label{sec:results}

\subsection{Experiment 1: Single-Crane Comparison}
\label{sec:exp1}

Table~\ref{tab:single} reports results on the 70 standard Lee instances. The original DRL model achieves a mean gap of FILLME--OM-GAP
\% (R-type: FILLME--OM-R
\%, consistent with the 7.8\% reported in~\cite{shin2026}), roughly one-third of the strongest heuristic's gap (Lin2015: FILLME--LIN-GAP
\%). The extracted ZeroShot policy reproduces these values exactly at $C=1$; the extraction loses nothing. Heuristic performance degrades with yard scale, while the DRL policy remains stable across scales.

\begin{table}[h!]
    \centering
    \caption{Single-crane comparison (70 standard Lee instances). Gap(\%) vs.\ the Theorem-2 bound of~\cite{shin2026}.}
    \label{tab:single}
    \begin{tabularx}{\textwidth}{lcccc}
        \toprule
        Method & Mean Gap(\%) & Std(\%) & Min(\%) & Max(\%) \\
        \midrule
        \textbf{Original Model~\cite{shin2026} $\equiv$ ZeroShot($C{=}1$)} & \textbf{FILLME--TAB1-OM}
 & & & \\
        Lin2015~\cite{lin2015} & FILLME--TAB1-LIN
 & & & \\
        Leveling~\cite{zehendner2017} & FILLME--TAB1-LEV
 & & & \\
        Kim2016~\cite{kim2016} & FILLME--TAB1-KIM
 & & & \\
        Durasevic2025~\cite{durasevic2025} & FILLME--TAB1-DUR
 & & & \\
        \bottomrule
    \end{tabularx}
\end{table}

\subsection{Experiment 2: Multi-Crane Strategy Comparison}

FILLME--EXP2-TEXT-AND-TABLE

\subsection{Experiment 3: Multi-Crane Baseline Comparison}

FILLME--EXP3-TEXT-AND-TABLE

\subsection{Statistical Analysis, Interference, and Speedup}

FILLME--STATS-TEXT-AND-TABLE

\section{Discussion}
\label{sec:discussion}

FILLME--DISCUSSION (rewrite after numbers: why transfer works, recommendation, limitations incl. timing-model simplifications, LB looseness for makespan, zero-shot-only)

\section{Conclusion}

FILLME--CONCLUSION

\section*{Data Availability}
Code, benchmarks (70 M-CRP layouts), and experimental results: \url{https://github.com/sutobode/Master}.

\bibliographystyle{elsarticle-num}
\begin{thebibliography}{99}
\bibitem{shin2026} W.-J. Shin, I. Choi, S.-H. Cho, H.-J. Kim, Learning to retrieve containers: A scale-diverse deep reinforcement learning approach for the container retrieval problem, Transportation Research Part C: Emerging Technologies 183 (2026) 105496.
\bibitem{lee2010} Y. Lee, Y.-J. Lee, A heuristic for retrieving containers from a yard, Computers \& Operations Research 37 (6) (2010) 1139--1147.
\bibitem{lin2015} D.-Y. Lin, Y.-J. Lee, Y. Lee, The container retrieval problem with respect to relocation, Transportation Research Part C: Emerging Technologies 52 (2015) 132--143.
\bibitem{kim2016} Y. Kim, T. Kim, H. Lee, Heuristic algorithm for retrieving containers, Computers \& Industrial Engineering 101 (2016) 352--360.
\bibitem{forster2012} F. Forster, A. Bortfeldt, A tree search procedure for the container relocation problem, Computers \& Operations Research 39 (2) (2012) 299--309.
\bibitem{cifuentes2020} C. D. Cifuentes, M.-C. Riff, G-CREM: A GRASP approach to solve the container relocation problem for multibays, Applied Soft Computing 97 (2020) 106721.
\bibitem{durasevic2025} M. {\DJ}urasevi{\'c}, M. {\DJ}umi{\'c}, F. J. G. Gala, Multitask genetic programming for automated design of heuristics for the container relocation problem, Engineering Applications of Artificial Intelligence 144 (2025) 110001.
\bibitem{zehendner2017} E. Zehendner, D. Feillet, P. Jaillet, An algorithm with performance guarantee for the online container relocation problem, European Journal of Operational Research 259 (1) (2017) 48--62.
\bibitem{caserta2012} M. Caserta, S. Schwarze, S. Vo{\ss}, A mathematical formulation and complexity considerations for the blocks relocation problem, European Journal of Operational Research 219 (1) (2012) 96--104.
\bibitem{shinkim2025} W.-J. Shin, H.-J. Kim, Advances in multi-crane scheduling: extended non-interference modeling and temporal-constraint-based valid inequalities, European Journal of Operational Research (2025). doi:10.1016/j.ejor.2025.10.032.
\bibitem{stahlbock2008} R. Stahlbock, S. Vo{\ss}, Operations research at container terminals: a literature update, OR Spectrum 30 (1) (2008) 1--52.
\bibitem{kool2019} W. Kool, H. van Hoof, M. Welling, Attention, learn to solve routing problems!, in: International Conference on Learning Representations, 2019.
\bibitem{kwon2020} Y.-D. Kwon, J. Choo, B. Kim, I. Yoon, Y. Gwon, S. Min, POMO: Policy optimization with multiple optima for reinforcement learning, Advances in Neural Information Processing Systems 33 (2020) 21188--21198.
\bibitem{legato2001} P. Legato, R. M. Mazza, Berth planning and resources optimisation at a container terminal via discrete event simulation, European Journal of Operational Research 133 (3) (2001) 537--547.
\bibitem{sammarra2007} M. Sammarra, J.-F. Cordeau, G. Laporte, M. F. Monaco, A tabu search heuristic for the quay crane scheduling problem, Journal of Scheduling 10 (4--5) (2007) 327--336.
\bibitem{zhang2002} C. Zhang, Y.-W. Wan, J. Liu, R. J. Linn, Dynamic crane deployment in container storage yards, Transportation Research Part B: Methodological 36 (6) (2002) 537--555.
\bibitem{vaswani2017} A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, {\L}. Kaiser, I. Polosukhin, Attention is all you need, Advances in Neural Information Processing Systems 30 (2017).
\bibitem{williams1992} R. J. Williams, Simple statistical gradient-following algorithms for connectionist reinforcement learning, Machine Learning 8 (3) (1992) 229--256.
\end{thebibliography}
\end{document}
